<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-",
  message = FALSE
)
library(ggplot2)
theme_set(theme_minimal())
```

# packagesurvey: Navigating the R package universe

**Author:** [Julia Silge](http://juliasilge.com/) <br/>
**License:** [MIT](https://opensource.org/licenses/MIT)

[![Build Status](https://travis-ci.org/juliasilge/packagesurvey.svg?branch=master)](https://travis-ci.org/juliasilge/packagesurvey)

There are now more than 11,000 packages on CRAN, and R users must approach this abundance of packages with effective strategies to find what they need and choose which packages to invest time in learning how to use. At useR!2017, I contributed to an [organized session](http://sched.co/AypJ) focused on discovering, learning about, and evaluating R packages. In preparation for that session, I ran a brief online survey in the spring of 2017 to ask R users how they currently discover and learn about R packages. This package contains the results of that survey.

## Installation

This package can be install from GitHub using devtools.

```{r, eval = FALSE}
devtools::install_github("juliasilge/packagesurvey")
```

## Data

The survey results are available in this package in the `package_survey` data object.

```{r package_survey}
library(packagesurvey)
data("package_survey")
```

There were `r n_distinct(package_survey$respondent)` respondents to the survey. You can easily explore how many respondents chose each answer.

```{r}
library(dplyr)

package_survey %>%
    mutate(total = n_distinct(respondent)) %>%
    count(answer, total) %>%
    arrange(desc(n)) %>%
    mutate(proportion = scales::percent(n / total)) %>% 
    select(-total, -n) %>%
    kable(col.names = c("How do you currently discover and learn about R packages",
                        "% of respondents who chose each answer"))
```

You might also be interested in when R users responded to the survey.

```{r}
package_survey %>%
    ggplot(aes(response_time)) +
    geom_histogram() +
    labs(x = NULL,
         y = "Number of R users",
         title = "Responses to survey on package discovery over time")
```


This project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.



